\documentclass[a4paper]{article}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{fullpage}

%\usepackage{doublespace}
%\setstretch{1.2}

\usepackage{ae}
\usepackage[T1]{fontenc}
\usepackage{CV}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
      linkcolor=blue,
    urlcolor=blue}

\begin{document}

\pagestyle{empty}

%Ueberschrift
\begin{center}
\huge{\textsc{Curriculum Vitae}}
\vspace{\baselineskip}

\Large{\textsc{Md.Faridul Islam Talukder}}\\
\end{center}
\vspace{1.5\baselineskip}

\section{Address}
\noindent
\begin{minipage}{.7\textwidth}
  Room No-105\\
  Fazlul Hauqe Muslim Hall\\
  University of Dhaka\\
  Dhaka-1000\\
\end{minipage}
\begin{minipage}{.7\textwidth}
  \faPhone{} +8801746-023450\\
  \faEnvelopeO{}  \href{mailto:al2helal@gmail.com}{al2helal@gmail.com}\\
\end{minipage}

\section{Personal Details}
\begin{CV}
  \item[Gender] Male 
  \item[Father] Md.Bablu Talukder
  \item[Mother] Most. Fensy Begum
  \item[Date of birth] 5th November, 1990
  \item[Permanet Address] Vill. Sataria, P.O. Sataria, P.Code-2050, Up. Sarishabari, Dist. Jamalpur
  \item[Nationality] Bangladeshi
  \item[Religion] Islam
  \end{CV}

\section{Career Objective}
\begin{CV}
\item To build up an efficient career in the teaching profession and thereby serve humanity.
  \end{CV}


\section{Education}

\begin{CV}
\item[2015-2016] University of Dhaka, Dhaka-1000.\\Receieved Master of Science Degree in Mathematics in 2017.\\Obtained CGPA 3.10 out of 4.00.
\item[2009-2010] University of Dhaka, Dhaka-1000.\\Receieved Bachelor of Science Degree in Mathematics in 2013.\\Obtained CGPA 2.67 out of 4.00.
\item[2008] Shahid Syed Nazrul Islam College, Mymensingh.\\Passed H.S.C (Science Group) under Dhaka Board in 2008.\\Obtained GPA 4.70 out of 5.00.
\item[2006] Riaz Uddin Talukder, Sarishabari, Jamalpur.\\Passed S.S.C (Science Group) under Dhaka Board in 2006.\\Obtained GPA 4.75 out of 5.00.
\end{CV}


%\section{Language Skills}
%\begin{table}[h] %\centering
%\begin{tabular}{p{2cm}>{}p{2.5cm}p{3cm}}
%Bangali  & native \\
%English  & 2nd language\\
%\end{tabular}
%\end{table}


%\begin{CV}
%\item Teaching.
%\end{samepage}
%\end{CV}
%\noindent \today
\end{document}
